Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/from-weak-separability-to-strong-separability.tex
Fixes

\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
satisfying \eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
$1$. We consider two cases regarding the relationship between $\gamma_1$ and
$\gamma_2$.

\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
multivariate polynomial $p_i:\R^d \to \R$

\begin{align*}
\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
\end{align*}
such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
(resp. $p_i(x) \leq -1/2$).
Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
 and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
\begin{align*}
&\norm{p_i} 
\\
& \le 
\left[
  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
\right]^{
  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
} \; . \\
\end{align*}
By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
\begin{align*}
&\norm{c_i}_{\ell_2}
\\
& \le 
\left[
  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
\right]^{
  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
} \; .
\end{align*}
Define vectors $u_i \in \ell_2$ as
\begin{align*}
u_i & = 
\frac{c_i/\sqrt{K}}{ 
  \left[
    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
  \right]^{
    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
  }
} \; . \\
\end{align*}

Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.

\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
we can show that
$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.
%The proof for the case of $\gamma_1 < \gamma_2$
%is symmetric.

In summary, the examples are strongly
linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
Finally, observe that for any $t=1,2,\dots,T$,
\[
k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
\qedhere
\]
\end{proof}

>>>>

%\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
%Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
%linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
%satisfying \eqref{equation:weak-linear-separability-1} and
%\eqref{equation:weak-linear-separability-2}.

%Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
%$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
%$1$. We consider two cases regarding the relationship between $\gamma_1$ and
%$\gamma_2$.

%\paragraph{Case 1: $\gamma_1 \geq \gamma_2$.} In this setting,
%Theorem~\ref{theorem:polynomial-approximation-1} implies that there exist a
%multivariate polynomial $p_i:\R^d \to \R$

%\begin{align*}
%\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
%\end{align*}
%such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
%(resp. $p_i(x) \leq -1/2$).
%Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
% and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
%\begin{align*}
%&\norm{p_i}
%\\
%& \le
%\left[
%  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
%\right]^{
%  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
%} \; . \\
%\end{align*}
%By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
%$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
%\begin{align*}
%&\norm{c_i}_{\ell_2}
%\\
%& \le
%\left[
%  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
%\right]^{
%  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
%} \; .
%\end{align*}
%Define vectors $u_i \in \ell_2$ as
%\begin{align*}
%u_i & =
%\frac{c_i/\sqrt{K}}{
%  \left[
%    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil
%  \right]^{
%    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
%  }
%} \; . \\
%\end{align*}

%Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$.
%Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$
%and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
%$\ip{u_j}{x_t} \le - \gamma_1$. In other words,
%$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
%strongly linearly separable with margin $\gamma_1 = \max\{\gamma_1, \gamma_2\}$.

%\paragraph{Case 2: $\gamma_1 \leq \gamma_2$.} Following the
%same idea as Case 1 and using Theorem~\ref{theorem:polynomial-approximation-1},
%we can show that
%$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
%strongly linearly separable with margin $\gamma_2 = \max\{\gamma_1, \gamma_2\}$.

%In summary, the examples are strongly
%linearly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
%Finally, observe that for any $t=1,2,\dots,T$,
%\[
%k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
%\qedhere
%\]
%\end{proof}
